---
title: "Exam 70-773 Analyzing Big Data with R Study Guide"
output: html_document
---

# Introduction
This document is a study guide for Microsfot Exam 70-773: Analyzing Big Data with Microsoft R.

I have used R a lot in the past, but never really played with Microsoft R or its predessor Revolution R. Whenever I need to do anything with 'big data' I would just use python or scala in Spark.

But I figured it would be a fun challenge to take 70-773, and since I've been using Azure a bunch lately, it makes sense to grab an MSCE, so I should be making a few more of these studyguides.

The format will follow the same topics as outlined toward the bottom of the [70-773 Exam Page](https://www.microsoft.com/en-us/learning/exam-70-773.aspx)

But first we have to set up our system

# Installing "Microsoft R"

Why is that in quotes? Because there apparently is no longer any such thing as "Microsoft R" at least not as a server anyway, unless you use Azure, which is kind of the only reason anyone uses microsoft R in the first place...  But I digress.

"Microsoft R" is now mostly called RevoScaleR and is included in the Microsoft Machine Learning Server. Microsoft ML also functions as a python and F-Sharp server. 

# Read and Explore Big Data
## Read supported data file formats
This is a bit vague, but they mention SAS and SPSS specifically, so we should probably highlight that syntax. 

Fortunately Machine Learning server comes with a bunch of sample data sets for just this purpose. Here is the [Documentation](https://docs.microsoft.com/en-us/machine-learning-server/r/how-to-revoscaler-data-import)
```{r}
list.files(rxGetOption("sampleDataDir"))
```

We'll just use one of those for syntax demostration. Grabbing the data is straightforward, but difficult to remember the syntax.

```{r}
txtSource <- file.path(rxGetOption("sampleDataDir"),"claims.txt")

```

Let's break that down a little, also remember we can always use ?<the function name> as a command in R to learn more, and it seems to work in Microsoft R as well

#### file.path

`?file.path` is a frequently used function in R to give us a platform independent file path. Anyone who has had to deal with confusion back and forward slashes can appreciate this.

In this case we are using the rxGetOption commmand to pull the directory of sample data stored on our local or remote machine.

#### rxOptions

`?rxOptions` now this is our first Microsoft R specific command, and it's a big one, it's used to set options for all the different attributes of a RevoScaler Session. It does not need to be called for every execution, just once per session. These are global configuration.

But the above example uses   `rxGetOption` not `rxOptions`, what's the difference? rxOptions is for setting options while rxGetOptions is for retreival of a single option parameter. In our case that is the current sample data directory.

Let's break down what's happening for some clarity.

```{r}
rxGetOption("sampleDataDir")
# Returns "C:/Program Files/Microsoft/ML Server/R_SERVER/library/RevoScaleR/SampleData"

rxGetOption("claims.txt")
# Returns NULL as this isn't a configuration option

file.path(rxGetOption("sampleDataDir"), "claims.txt")
# Returns "C:/Program Files/Microsoft/ML Server/R_SERVER/library/RevoScaleR/SampleData/claims.txt"

```
So all we are do


### Reading and writing to SQL

https://docs.microsoft.com/en-us/machine-learning-server/r/sample-built-in-data
